Append-only Datastore

### 2020-06-08 paper/paper.tex
Proofread
Fixes to grammar, spelling, a little meaning.

\title{Append-only Datastore}
\author{
	Mingyan Zhao
	\and
	Steven Tung
	\and
	Kevin Krakauer
}
\date{}

@@

\section*{}
We built an eventually consistent, append-only datastore focused on low
read/write latency and high availability. In the common case, clients interact
only with nearby nodes for extremely low latency. We do not provide overwrite
and delete operations. This simple interface guarantees properties making client
implementation simple: the relative order of data for a given key is consistent
and each client communicates only with a single node.

The datastore is eventually consistent. Data is stored in memory for low latency
and in local disk for safety. Nodes can operate when disconnected from the
system, preserving availability in the face of total and long-term partitioning.
We believe this system will be useful in chat and distributed logging
applications.

\section{Introduction}
As organizations increasingly move to the cloud, applications are designed from
the ground up with a distributed architecture (in some cases referred to as
\textit{microservices}). Despite numerous advantages, distributed
application design requires addressing latency and partitioning concerns that
monolithic applications do not have (or in the case of partitioning, are not
solvable).

Our \textit{append-only datastore} addresses latency and partitioning concerns
for append-only workloads. It is designed to run as a service distributed
globally across multiple data centers. By explicitly distinguishing between a
\textit{leader} node and \textit{follower} nodes, we gain several advantages
over other eventually consistent systems:

\begin{enumerate}
	\item Clients communicate only with their nearest follower for extremely
		low latency.
	\item Followers provide linearizability for client appends on a single
		key. That is, all clients writing to the same key of the same
		follower will see linearized writes.
	\item Eventual consistency is minimally disruptive to clients. A client
		may read the data for key $k$ and receive data consisting of 2
		writes' data: $d_1, d_2$. Write $x$ with data $d_x$ sent through another follower
		preserves the ordering of $d_1$ and $d_2$, so the system
		eventually returns $d_x, d_1, d_2$, $d_1, d_x, d_2$, or $d_1,
		d_2, d_x$ when read.  Because of (2), writes directly to the
		same follower are linearizable.
\end{enumerate}

We also gain the advantages of some more traditionally eventually consistent
systems, such as great partition tolerance \cite{dynamo}. Together, these
properties are highly desirable for many append-only applications. Consider the
following:

\begin{itemize}
	\item \textbf{Chat} - Chat applications are inherently append-only. Users
		in different parts of the globe expect near-instantaneous (only
		a few seconds) latency. Users in the same building, however,
		expect to receive messages instantaneously. Think of a global
		company: teammates send messages and links to nearby teammates,
		expecting them to arrive immediately. Consider a chatroom
		occupied by a team in North American and a team in Asia. Each
		team member sees their local peers' messages immediately and in
		exactly the order that they are sent. It's acceptable for the a
		message from the other team to take a bit longer and appear
		slightly out of order in the logged chat.
	\item \textbf{Distributed logging} - Consider a distributed application
		running in multiple data centers on multiple continents. The
		application is monitored in real time in each datacenter. Logs
		are write-only, and critical for monitoring. By using the
		append-only datastore for logging, the monitoring service:
		\begin{itemize}
			\item Continues operating when a datacenter is
				partitioned from the rest of the system.
			\item Receives logs with extremely low latency from the
				nearby monitored application.
			\item Has an eventually consistent log that can be
				stored for later analysis and debugging.
		\end{itemize}
	% \item \textbf{Distributed data processing}
\end{itemize}

\section{Design}
% TODO: Add architecture diagram.
Nodes in the append-only datastore are classified in a simple hierarchy as seen
in TODO(add the architecture diagram). A single \textit{leader} directs multiple
\textit{followers}. Clients connnect to and communicate with a nearby follower,
likely running in the same datacenter, to minimize latency. Our design tolerates
arbitary partitions between nodes and ensures an eventually consistent view of
data.

Clients are exposed the following API by followers:
\begin{itemize}
	\item \texttt{append(key, data)} - Appends \texttt{data} to the existing
		data for \texttt{key}. Guarantees that \texttt{data} appears
		after any data that the client already read for \texttt{key}.
	\item \texttt{get(key)} - Gets the data for \texttt{key}, expressed as a
		list of indexed values. For example, the returned data will be
		the result of writes 1, 3, and 5, expressed as $\{d_1, d_3,
		d_5\}$. Subsequent \texttt{get} requests will always return
		$d_1$, $d_3$, and $d_5$ in the same relative order, but other
		writes may be prepended, appended, or interspersed.
\end{itemize}

\subsection{Follower}
% Explain what happens when this is partitioned.
% Explain read-your-own-writes consistency.
% Be sure to discuss any synchronization that happens here, as the follower is
% responsible for synchronizing its the writes to it.
The follower is our most complex component. Its responsibilities include:

\begin{itemize}
	\item Handing \texttt{append} and \texttt{get} requests from clients.
	\item Ordering appends.
	\item Updating the master about appended data.
	\item Receiving the eventual, global ordering of data from the master
		and imposing it on data.
	\item Syncing with other followers to communicate updates and orderings.
\end{itemize}

% TODO: We don't actually do the update-on-get thing yet.
Each follower stores the entire datastore locally in memory. When clients issue
\texttt{get(k)} requests, these are served from the in-memory datastore to minimize
response latency. It also causes the follower to ask the leader for the most
up-to-date data for \texttt{k}, ensuring that frequently accessed data is kept
relatively fresh.

\texttt{append} requests are also fast, limited by the speed of a local disk
write. When a client appends data to key \texttt{k}, the follower writes that
data - along with its index - to local disk before returning to the client. This
ensures that data is not lost upon crashing and rebooting. For increased fault
tolerance, the append should be written to multiple disks locally or to a remote
disk. Note that throughout this section when we refer to updating local storage,
the in-memory store is also updated immediately after data is written to disk.

As soon as the append is written to disk, the follower (concurrently with
replying to the client) sends an \texttt{update} request to the leader
containing the key being appended to and the index that the follower has
assigned the appended data. The leader resolves and orders the append with any
other concurrent appends from different followers (see next section), and
responds.

There are two types of responses. The first - and likely most common - case
is a simple \texttt{SUCCESS} response. This indicates that the append completed
successfully and the follower has up-to-date data for that key. The second is a
\texttt{NEEDS\_UPDATE} response. This indicates that the data was appended, but
another \texttt{update} preempted it. In this scenario, the follower changes the
locally stored index of the appended data, and sends a \texttt{sync} request
another follower indicated by the leader's response.

Followers use the \texttt{sync} request to get data they are missing,
effectively ``patching the holes" in their local datastore. This ensures the
eventually consistent property of the system.

\subsubsection{Common Case}
When updates do not overlap, the follower handles \texttt{append} requests as
follows:

\begin{enumerate}
	\item Write the append to local storage along with the index \texttt{i}
		the follower believes applies to the append.
	\item Respond to the client that the request was successful.
	\item Concurrently with (2), send an \texttt{update} to the leader that
		an append occured on key \texttt{k} at index \texttt{i}.
	\item The leader responds with \texttt{SUCCESS}.
	\item The follower updates local disk to indicate that the append has
		been commited at index \texttt{i} by the leader.
\end{enumerate}

The data for key \texttt{k} has simply benn appended to, changing from $\{d_a,
d_b, d_c, ..., d_{i-1}\}$ to $\{d_a, d_b, d_c, ..., d_{i-1}, d_i\}$, where $a < b <
c < i$. Note that there may be data ``holes" between $a$, $b$, $c$, and $i$ not
yet filled in by either a \texttt{get} or \texttt{sync}.

\subsubsection{Conccurent Updates}
When concurrent updates occur:

% TODO: There's some ugly mixing of texttt and math notation here, particularly
% around i'.
\begin{enumerate}
	\item The same as steps 1-3 above.
	\item The leader responds with \texttt{NEEDS\_UPDATE}.
	\item The follower updates local disk to indicate that the append has
		been commited at index \texttt{i`} by the leader.
	\item The follower sends a \texttt{sync} request to the follower that
		appended the data at index \texttt{i`-1}, as indicated in the
		leader's response.
	\item The follower receives and stores on local disk the data it was
		missing, including what the leader deemed to be the ``winner" of
		index \texttt{i}.
\end{enumerate}

The data for key \texttt{k} in this case is an append and a reordering,
changing from $\{d_a, d_b, d_c, ..., d_{i-1}\}$ to $\{d_a, d_b, d_c, ...,
d_{i-1}, d_i, d_{i'}\}$, where $a < b < c < i$ and as above may have more holes
to fill.

% TODO: We don't yet implement the early return of data.
It is possible for a chain of \texttt{sync} requests to form when more than 2
followers append a key at the same time. If follower $a$ starts syncing with
follower $b$, which is already waiting on follower $c$ to respond to a
\texttt{sync}, $b$ will send what is knows to $a$. $a$ then retries to get
missing data, at which point $b$ waits to respond until it has new data to send.

\subsubsection{Follower Fault Tolerance}
Both \texttt{update} and \texttt{sync} requests are retried in case of network
failure. If a follower reboots during a \texttt{update}, it can inspect the disk
at boot and see that it has appended data locally that has not been confirmed by
the leader. If a follower reboots during a \texttt{sync}, it will have stale
data until a \texttt{get} or \texttt{append} causes it to update. This keeps the
system simple while retaining its consistency properties.

\subsection{Leader}
% Explain what happens when this is partitioned.
% Reference GFS and not transporting the data itself.
It synchronizes stuff.

\subsection{Clients}
% Describe the API and guarantees exposed to clients.
We have very distinguished clientele.

\subsection{Corner Cases}
% Multiple simultaneous writes from c1 and c2 to f1. How do we ensure that the
% GL does not order w2 before w1?
% What if the sync request can be partially satisfied. Do we not respond, or
% respond partially and expect another sync request from the same follower?

\section{Implementation}

\section{Evaluation}
We tested using some super cool gcloud stuff.

\subsection{Workload 1}
Oh wow, we're so fast.

\subsection{Workload 2}
Oh no, we're unexpectedly not that fast.

\section{Related Work}
% Talk about Kafka
This is the most filler of all filler sections. Look, a reference! \cite{dynamo}

\section{Future Work}
% Use a raft group instead of a single node for each follower and GL.
% Client fallback to other followers.
Make it actually work.

\section{Conclusions}
I'd just like everyone to pat themselves on the back here.

\bibliography{paper} 
\bibliographystyle{ieeetr}

>>>>

\usepackage{graphicx}
\usepackage{subfigure}

\title{Append-only Datastore}
\author{
	Mingyan Zhao \\
    myzh@stanford.edu
	\and
	Steven Tung\\
    steven.tung@stanford.edu
	\and
	Kevin Krakauer\\
    kevinkrakauer@gmail.com
}
\date{}

@@

\section*{Abstract}
We built an eventually consistent, append-only datastore focused on low
read/write latency and high availability. In the common case, clients interact
only with nearby nodes for extremely low latency. Data is always appended to the 
store for a given key and the relative order of observed data is maintained.

The datastore is eventually consistent. Data is stored in memory for low latency
and in local disk for safety. Nodes can operate when disconnected from the
system, preserving availability in the face of total and long-term partitioning.
We believe this system will be useful in chat, social media, and distributed
logging applications.

\vspace{-0.4cm}
\section{Introduction}
\vspace{-0.2cm}
As organizations increasingly move to the cloud, applications are designed from
the ground up with a distributed architecture (\textit{microservices}). Despite
numerous advantages, distributed application design requires addressing latency
and partitioning concerns that monolithic applications do not have.

Our \textit{append-only datastore} addresses latency and partitioning concerns
for append-only workloads. It is designed to run as a service distributed
globally across multiple data centers. By explicitly distinguishing between a
\textit{leader} node and \textit{follower} nodes, we gain several advantages
over other eventually consistent systems:
\begin{enumerate}
	\item Clients communicate only with their nearest follower for extremely
		low latency. \vspace{-0.3cm}
	\item Eventual consistency is minimally disruptive to clients. A client
		may read the data for key $k$ and receive data consisting of 2
		writes' data: $\{d_1, d_2\}$. Write $x$ with data $d_x$ sent
		through another follower preserves the ordering of $d_1$ and
		$d_2$, so the system eventually returns $\{d_x, d_1, d_2\}$,
		$\{d_1, d_x, d_2\}$, or $\{d_1, d_2, d_x\}$ when read.
\end{enumerate}
We also gain the advantages of some more traditionally eventually consistent
systems, such as great partition tolerance \cite{Dynamo}. Together, these
properties are highly desirable for many append-only applications. Consider the
following:

\begin{itemize}
	\item \textbf{Distributed logging} - Consider a monitoring service using
		the append-only datastore for logs in real time. The service
		writes and retrieves logs with extremely low latency from the
		nearby data center. Also it is provided an eventually consistent
		log that contains data from all of the deployments.
	\item \textbf{Chat Application} - Consider a chatroom
		occupied by a team in North America and a team in Asia. Each
		team member sees their local peers' messages immediately, and
		all messages eventually.
\end{itemize}

\section{Related Work}
Amazon's Dynamo \cite{Dynamo} supports always-writable semantics, high partition
tolerance, and laser-focuses on low-latency operation. Unlike our system, Dynamo
is a key-value store. It also exposes a great deal of complexity to developers,
who must tailor their use of Dynamo such that conflicts are resolvable and
must manually implement conflict resolution in clients. Our system does not
allow for conflicts. Google's GFS \cite{GFS} is also optimized for append-heavy workloads and uses a
single master for simplicity and intelligent coordination. It supports random
writes as well. However, it is explicitly optimized for non-latency-sensitive
applications, and a single read can require multiple hops (the GFS master and
chunkserver). LinkedIn's Kafka \cite{Kafka} provides eventual delivery of large
quantities of data, but running under a publish/subscribe
mechanism.

\vspace{-0.4cm}
\section{Design}
Nodes in the append-only datastore are classified in a simple hierarchy as seen
in Figure \ref{Architecture}. A single \textit{leader} directs multiple
\textit{followers}. Clients connect to and communicate with a nearby follower,
likely running in the same data center, to minimize latency. Our design tolerates
arbitrary partitions between nodes and ensures an eventually consistent view of
data.
%\vspace{-0.4cm}
% Architecture
\begin{figure}[t]
\includegraphics[width=8cm]{figure/SystemStructure.pdf}
\caption{Architecture}
\label{Architecture}
\end{figure}
Clients are exposed to the following API by followers:
\begin{itemize}
	\item \texttt{append(key, data)} - Appends \texttt{data} to the existing
		data for \texttt{key}. Guarantees that \texttt{data} will be
		committed eventually if it is written to local disk.
	\item \texttt{get(key)} - Gets the data for \texttt{key}, represented as a
		list of values. Later calls to \texttt{get} return data in the
		same relative order, but other data may be interleaved or
		appended.
\end{itemize}

\subsection{Leader}
% TODO: Explain what happens when this is partitioned. Look at gfs paper.
The leader is responsible for globally ordering writes for each key. Like GFS's
master \cite{GFS}, it only stores metadata rather than the value itself.
This decreases network usage.  Also, the
burden on disks is lighter per update, increasing writes per second and the
average lifetime of each disk. The simplicity of a single master
simplifies our implementation and the rest of our design, which increases
the overall stability of the system.

\subsubsection{Index number}
The leader maintains the latest index number for all keys. Index numbers are
globally unique and monotonically increasing. Once generated, each is mapped
to a list of values on the requesting follower. If another follower needs that
value, it simply needs the index number to fetch the data.

\vspace{-0.4cm}
\subsubsection{Update}
Upon receiving an \texttt{Update} request, the leader advances the index
number by one and updates the follower information to the incoming one.

The \texttt{Leader} decides whether the requesting follower needs to sync up
with other followers. If a mapping exists from key $k$ to index $i$, an
\texttt{Update} carrying the same index $i$ does not need a Sync ($i$ still
increments by 1). This may happen when 1) a key created on the leader for the
first time, or 2) the requesting follower is the same as the recorded follower
for the key.

An \texttt{Update} to $i' < i$ indicates that the sender does not have the
latest data. In this case the leader signals the follower to sync with the
follower in its records that originated the append at index $i$. This may happen
when two followers are append data to the same key concurrently. The common,
non-concurrent case is shown in Figure \ref{CommonUpdate}.

% update procedure figure
\begin{figure}[h]
\includegraphics[width=8cm]{figure/update.pdf}
\caption{Update procedure}
\label{CommonUpdate}
\end{figure}

\vspace{-0.3cm}
\subsubsection{Broadcasting index numbers}
The leader broadcasts ensure the eventual consistency of the system. Each
appended value gets replicated and synced immediately between the requesting
followers and in-record follower, but all of the other followers do not know
it until the leader broadcasts the latest index number.

Depending on the workload and use cases, we provide different ways of
broadcasting. One is triggered per-request, which is expected to provide lower
consistency latency but may only be used in a lower QPS scenario, since the
broadcasting may cause a great amount of communication between the followers.
The other one is triggered periodically, which is expected to be used in most
cases. The leader broadcasts the updated keys and their index numbers repeatedly
at a small, set interval.

\subsubsection{Leader Fault Tolerance}
Because the leader writes all updates to disk, it tolerates crashes and reboots.
For greater fault tolerance, it should write to multiple disks or a remote disk
as well.

The system continues to function when the leader is partitioned, but followers
and thus clients do not receive updates from other followers. As long as the
partition is eventually healed, the system will propagate information correctly
and self-heal. If for some reason there is a permanent partition, it must be
manually worked around by changing the cluster configuration (i.e. the set of
nodes in the system).

\subsection{Follower}
% Explain what happens when this is partitioned.
% Explain read-your-own-writes consistency.
% Be sure to discuss any synchronization that happens here, as the follower is
% responsible for synchronizing its the writes to it.
The follower is our most critical component. Its responsibilities include:

\begin{itemize}
	\item Handing \texttt{append} and \texttt{get} requests. \vspace{-0.4cm}
	\item Managing data. \vspace{-0.4cm}
	\item Updating the leader about appended data. \vspace{-0.4cm}
	\item Syncing with other followers to communicate updates and orderings.
\end{itemize}

\subsubsection{Data structure}
Followers replicate the entire datastore in memory to minimize
reading and writing latency. The data structure is described in Figure \ref{DataStructure}.

% data structure figure
\begin{figure}[h]
\includegraphics[width=8cm]{figure/DataStructure.pdf}
\caption{Data procedure on Follower}
\label{DataStructure}
\end{figure}

\subsubsection{Client Interfaces}
\textbf{Append(key, data):} Upon reviving an \texttt{Append} request, the
follower writes the data to memory first and then writes to a local disk for data
safety. It returns immediately after the data is written to local disk. For
increased fault tolerance, the append should be written to multiple disks
locally or to a remote disk. Note that throughout this section when we
refer to updating local storage, the in-memory store is also updated immediately
after data is written to disk.

The follower always appends data to the pre-update-buffer first, then issues an
\texttt{Update} if the pre-update-buffer is not empty. If it receives an
\texttt{Update} response with a index number, it creates a new index entry and
moves all of the data from pre-update-buffer to the new entry.

\noindent \textbf{Get(key):} When clients issue a \texttt{Get} request, they are
served from the in-memory datastore. We guarantees that the data read by the
clients are correct, but not necessarily yet globally consistent. The follower
builds up a list with all of the data from each index as well as everything from
the pre-update-buffer.

\subsubsection{Synchronization}
Followers use the \texttt{Sync} request to get data they missed. This ensures
the eventual consistency of the system. \texttt{Sync} requests also signal what
data the sender has to the recipient, enabling the recipient to create new index
entries in its local datastore. The \texttt{Sync} request is issued when a
follower receives an \texttt{Update} response from the leader indicating it
needs synchronization.

Since a follower may missing multiple indices of data, a \texttt{Sync} request
may carry a list of indices that it is asking for. However the recipient may
also be missing some of the indices if there is a large amount of \texttt{Sync}
requests in flight simultaneously. To mitigate this, the \texttt{Sync} response
only replies with indices and data the recipient already has, so that the
issuer can accept what is returned and do another \texttt{Sync} asking for
what is left. Eventually, each follower synchronizes with and achieves global
consistency.

Combined with the \texttt{Update} requests, Figure \ref{UpdateAndSync}
demonstrates a message flow of synchronization in common case.

% UpdateAndSync figure
\begin{figure}[h]
\includegraphics[width=8cm]{figure/UpdateAndSync.pdf}
\caption{Update and Sync message flow}
\label{UpdateAndSync}
\end{figure}

\subsubsection{Follower Fault Tolerance}
Both \texttt{Update} and \texttt{Sync} requests are retried in case of network
failure. If a follower reboots during a \texttt{update}, it can inspect the disk
at boot and see that it has appended data locally that has not been confirmed by
the leader. If a follower reboots during a \texttt{sync}, it will have stale
data until a \texttt{get} or \texttt{append} causes it to update. This keeps the
system simple while retaining its consistency properties.

\vspace{-0.4cm}
\section{Evaluation}
The system is written in Go and can be run manually or distributed and
run with Docker. Nodes communicate via gRPC.

We ran tests with a cluster of Google Compute Engine virtual machines. Google
Cloud platform provides internal IP communication between VM instances, which
means request between servers do not go through the public Internet and are thus
fast. We deployed our system in the following locations.
\begin{itemize}
    \vspace{-0.4cm}
	\item One leader in Iowa, Central USA.
	\vspace{-0.4cm}
	\item One follower and one client in each of the following five locations
\vspace{-0.3cm}
    \begin{itemize}
    \item Iowa, central USA.
\vspace{-0.3cm}
	\item Los Angeles, west USA.
\vspace{-0.3cm}
	\item South Carolina, east USA.
\vspace{-0.3cm}
    \item London, west Europe.
\vspace{-0.3cm}
    \item Tokyo, northeast Asia.
\vspace{-0.3cm}
    \end{itemize}
\end{itemize}

In the performance test, each client in the performance test sends 120,000
\texttt{Append} against 10 keys randomly, so that in total there are
600,000 values in the datastore globally. After all of the \texttt{Appends} are
done, each client then retrieves the data by issuing \texttt{Get} for all of the
10 keys every 0.5 second periodically.

\subsection{Append Request Performance} We measures the \texttt{Append} request
latency in Table \ref{AppendLatency}.  The result shows that \texttt{Append} is
extremely fast, about 7.5 milliseconds on average. The 600,000 requests can be
done in a little less than 1 second due to appending only involving
communication with a single node.

\begin{table}[h]
\small
\centering 
\begin{tabular}{ |p{1.6cm}|p{1cm}|p{0.8cm}|p{0.8cm}|p{1cm}|p{0.8cm}|  }
\hline
Location & S. C. & Tokyo & Iowa & London & L.A. \\
 \hline
 1 Req   & 8.06 & 7.91 & 8.23 & 7.82 & 7.94\\
\hline
600k Req & 967.62 & 948.72 & 988.00 & 938.75 & 952.92\\
 \hline
\end{tabular}
\caption{Append request latency in millisecond (S.C. for South Carolina, L.A. for Los Angeles)}
\label{AppendLatency}
\end{table}

 \vspace{-0.5cm}
\subsection{Eventual consistency}
One critical result is the eventual consistency, since this is what we trade off
for the low latency read and write. The result is shown in Figure
\ref{ConsistencyDelay}. After 0.5 seconds, all of the followers have already
begun syncing with each other and received some of the data from each other. The
start point is different since the clients were started sequentially. After 2.0
seconds, the follower deployed in South Carolina finished synchronization and
received all of the 600,000 values. After 3.5 seconds, all of the follower held
all of the data and the system reached eventual consistency.

% Consistency delay figure
\begin{figure}[h]
	\subfigure[Eventual Consistency Delay]{\label{fig:c}
		\includegraphics[width=8cm]{figure/consistency.pdf}}
	\subfigure[Get Request Latency.]{\label{fig:g}
		\includegraphics[width=8cm]{figure/GetRequestLatency.pdf}}
\caption{Performance Test Result}
\vspace{-0.4cm}
\label{ConsistencyDelay}
\end{figure}

\subsection{Get Request Performance}
The result of the \texttt{Get} is shown in Figure \ref{ConsistencyDelay}.
Latency starts differently because the Follower held different amount of data.
After 3.5 seconds, the latency of different Followers converged to between 90
milliseconds and 100 milliseconds. Note that the implementation of \texttt{Get}
could be optimized to achieve better performance.

% Get request delay figure
%\begin{figure}[h]
%\includegraphics[width=8cm]{figure/GetRequestLatency.pdf}
%\caption{Get Request Latency}
%\label{GetRequestLatency}
%\end{figure}
\vspace{-0.4cm}
\section{Future Work}
We could greatly increase throughput by providing a client library (rather than
a raw GRPC interface) that is aware of the indices or latest index it holds.
This would enable followers to selectively return only the few pieces of data a
client is missing rather than all the data.

To increase fault tolerance, we have discussed making each follower and the
leader their own small cluster of consensus nodes. This would greatly increase
fault tolerance and, while it may complicate the system, would not complicate
clients or the protocols via which nodes communicate.

Lastly, there may be cases where followers fail or are partitioned from their
nearby clients. In these cases, we would like to explore whether clients can
fall back to another follower.
\vspace{-0.3cm}
\section{Conclusions}
We built a datastore to provide low latency and high availability for append-only
data storage. While this work is tailored to a specific set of workloads, there
are numerous applications that can benefit from this approach.

Our system can be used to support distributed services such as distributed
monitoring and chat applications with high performance. Importantly, it exposes
a simple interface allowing for simple clients. We believe that this makes it a
useful tool in building distributed and microservice systems.
\vspace{-0.4cm}
\bibliography{paper} 
\bibliographystyle{ieeetr}
